Scoring epidemiological forecasts on transformed scales

### 2023-08-15 final submission after reformatting/final-manuscript.tex
change Figure to Fig and add a single bib file

Across the dataset, the average number of observed cases and deaths varied considerably by location and target type (see Fig \ref{fig:HUB-mean-locations}A and B). On the natural scale, scores show a pattern quite similar to the observations across targets (see Figure\ref{fig:HUB-mean-locations}D) and locations (see Figure\ref{fig:HUB-mean-locations}C). On the log scale, scores were more evenly distributed between targets (see Figure\ref{fig:HUB-mean-locations}D) and locations (see Figure\ref{fig:HUB-mean-locations}C). Both on the natural scale as well on the log scale, scores increased considerably with increasing forecast horizon (see Fig \ref{fig:HUB-mean-locations}E). This reflects the increasing difficulty of forecasts further into the future and, for the log scale, corresponds with our expectations from Section \ref{sec:methods:growthrate}.

@@

\clearpage
\bibliography{../bib/log-or-not-v2.bib, ../bib/log-or-not.bib, ../bib/software.bib}
\end{document}

>>>>

Across the dataset, the average number of observed cases and deaths varied considerably by location and target type (see Fig \ref{fig:HUB-mean-locations}A and B). On the natural scale, scores show a pattern quite similar to the observations across targets (see Fig \ref{fig:HUB-mean-locations}D) and locations (see Fig \ref{fig:HUB-mean-locations}C). On the log scale, scores were more evenly distributed between targets (see Fig \ref{fig:HUB-mean-locations}D) and locations (see Fig \ref{fig:HUB-mean-locations}C). Both on the natural scale as well on the log scale, scores increased considerably with increasing forecast horizon (see Fig \ref{fig:HUB-mean-locations}E). This reflects the increasing difficulty of forecasts further into the future and, for the log scale, corresponds with our expectations from Section \ref{sec:methods:growthrate}.

@@

\clearpage
\bibliography{final-manuscript.bib}
\end{document}
